Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-18 analysis/analyse_rnaseq1.Rmd
fig 1c panel png

pdf("fig1_HPOdn.pdf",width=7, height=7)
plot(-log10(mg$pvalue.x),-log10(mg$pvalue.y),
  ylim=c(0,7), xlim=c(0,7), pch=19,
  main="SRP128998 HPO down",
  xlab="-log10 p-value (original)", ylab="-log10 p-value (corrected)")

>>>>

# PNG
png("fig1_HPOdn.png")

dev.off()

# PDF
pdf("fig1_HPOdn.pdf",width=7, height=7)
plot(-log10(mg$pvalue.x),-log10(mg$pvalue.y),
  ylim=c(0,7), xlim=c(0,7), pch=19,
  main="SRP128998 HPO down",
  xlab="-log10 p-value (original)", ylab="-log10 p-value (corrected)")
